### 2017-07-24 doc/manual/version3/inputParameters.tex
Initial commit. Added sensitivity inputs to manual, globalVariables, readInput, and validateInput.

>>>>

\section{The \texttt{sensitivityOptions} namelist}

\param{sensitivityOption}
{integer}
{0}
{When {\ttfamily geometryScheme == 5} and {\ttfamily includePhi1 == .false.}}. \\
{\ttfamily sensitivityOption} == 0: No sensitivity output computed. \\
{\ttfamily sensitivityOption} == 1: Sensitivity computed for VMEC harmonics using adjoint equation. The quantities of interest for sensitivity computations are specified by {\ttfamily AdjointRHSOption} and {\ttfamily AdjointRHSSpeciesOption}. \\

\param{AdjointRHSOption}
{integer}
{0}
{When {\ttfamily geometryScheme == 5} and {\ttfamily sensitivityOption == 1}} \\
{\ttfamily AdjointRHSOption == 0}: Sensitivity is computed for bootstrap current, particle flux, and heat flux. \\
{\ttfamily AdjointRHSOption == 1}: Sensitivity is computed for just bootstrap current. \\
{\ttfamily AdjointRHSOption == 2}: Sensitivity is computed for just particle flux. \\
{\ttfamily AdjointRHSOption == 3}: Sensitivity is computed for just heat flux.

\param{AdjointRHSSpeciesOption}
{integer}
{-1}
{When {\ttfamily geometryScheme == 5} and {\ttfamily sensitivityOption == 1} and {\ttfamily AdjointRHSOption /= 0}} \\
{\ttfamily AdjointRHSSpeciesOption == -1}: Sensitivity computed for output quantities specified by {\ttfamily AdjointRHSOption} for all species. \\
{\ttfamily AdjointRHSSpeciesOption >= 0}: Sensitivity computed for output quantities specified by {\ttfamily AdjointRHSOption} for species {\ttfamily AdjointRHSSpeciesOption}. \\
